Query Optimization for Dynamic Imputation

### 2017-05-10 paper/algorithm.tex
paper: add section labels

\subsubsection{Cardinality estimation}
The computation of $\textsc{Time}(q)$ and $\textsc{Penalty}(q)$ rely accurate cardinality estimates for the plan $q$ and its sub-plans.
These cardinality estimates are impacted not just by filtering or joining, as in the traditional relational algebra, but also by the imputation operators.
For example, a drop operator will reduce the cardinality of the result while an impute operator will maintain the same cardinality as the input.

@@

\subsubsection{Imputation quality}
We estimate the quality of the imputations in a plan $q$ using a heuristic measure $\text{Penalty}(q, P)$, which is computed as follows.

>>>>

\subsubsection{Cardinality estimation}
\label{sec:cardinal}
The computation of $\textsc{Time}(q)$ and $\textsc{Penalty}(q)$ rely accurate cardinality estimates for the plan $q$ and its sub-plans.
These cardinality estimates are impacted not just by filtering or joining, as in the traditional relational algebra, but also by the imputation operators.
For example, a drop operator will reduce the cardinality of the result while an impute operator will maintain the same cardinality as the input.

@@

\subsubsection{Imputation quality}
\label{sec:quality}
We estimate the quality of the imputations in a plan $q$ using a heuristic measure $\text{Penalty}(q, P)$, which is computed as follows.
